### 2021-10-07 abstract.latex/abstract.tex
fix .gitignore issue

\documentclass[12pt]{report}
\usepackage{amsmath}
\usepackage{bbm}
\usepackage{tabularx}
\usepackage{amsfonts}
\usepackage{hyperref}
\usepackage{tikz}
\usetikzlibrary{arrows.meta}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{listings}
%\usepackage[%
    %style=numeric, 
    %sorting=none,
    %doi=false,
    %url=false,
    %giveninits=true,
    %eprint=false,
    %isbn=false,
    %clearlang=true,
    %date=year,
    %hyperref]{biblatex}
\usepackage[style=phys,biblabel=brackets,maxbibnames=3]{biblatex}
%\renewbibmacro{in:}{%
  %\ifentrytype{article}{}{\printtext{\bibstring{in}\intitlepunct}}}
\DefineBibliographyStrings{english}{%
  bibliography = {References},
}

@@

\newcommand{\logchi}{7.4 }
\newcommand{\powchi}{8.8 }

\addbibresource{library.bib}

\newcommand{\e}{\vec e}
\newcommand{\half}{\frac{1}{2}}
\newcommand{\codeexample}[1]{
    \section{\texttt{#1}}
    \lstinputlisting[language=C++]{../code/cpp_code/#1}
}

@@

\begin{document}
\setlength{\baselineskip}{24pt}
\begin{titlepage}
\LARGE
\begin{center}
    {\bf Topology of the $O(3)$ non-linear sigma model under the gradient flow}\\[2.3cm]

\normalsize
A thesis submitted in partial fulfillment of the requirement \\
for the degree of Bachelor of Science with Honors in \\
Physics from the College of William and Mary in Virginia,\\[0.5cm]
by\\[0.5cm]
Stuart Thomas \\[2.5cm]
\end{center}
\normalsize
\begin{flushright}
\hfill Accepted for Honors \\[.5cm]
\hfill \hrulefill \\
\hfill \hfill Advisor: Prof. Christopher J. Monahan\\[.6cm]
\hfill \hrulefill \\Prof. Todd Averett \\[.6cm]
\hfill \hrulefill \\Prof. Andreas Stathopoulos \\[.6cm]
\end{flushright}
\begin{center}
Williamsburg, Virginia\\
May 2021
\end{center}
\end{titlepage}

\setlength{\topmargin}{0.0in}

\pagenumbering{roman}
\tableofcontents
\chapter*{Acknowledgments}
\addcontentsline{toc}{chapter}{Acknowledgments}
\paragraph
\indent I would like to thank my advisor, Professor Christopher Monahan. His constant helpfulness has made this research possible and enjoyable. I would also like to thank the entire faculty of the William \& Mary Physics Department. The amount of knowledge and wisdom they have given me has been beyond my imagination.

I would like to acknowledge the help of the High Performance Computing group at William \& Mary, whose cluster performed many of these simulations. I also want to acknowledge the financial help of the 1693 Scholars Program which funded preliminary research over the summer.

Finally, I would like to thank my friends and family who helped me reach this point in my academic and personal journey.

\listoffigures
\addcontentsline{toc}{chapter}{List of Figures}
\listoftables
\addcontentsline{toc}{chapter}{List of Tables}

\begin{abstract}
\setcounter{page}{5}
\addcontentsline{toc}{chapter}{Abstract}
\paragraph
\indent Quantum field theory is an extraordinarily successful framework that describes phenomena in particle physics and condensed matter. The $O(3)$ non-linear sigma model (NLSM) is a specific theory used in both of these fields, describing ferromagnets and acting as a prototype for the strong nuclear force. It features topologically stable configurations known as instantons which cannot continuously evolve to the ground state. The topological susceptibility is a parameter that describes this stability and is predicted to vanish in physical theories, however numerical simulations find that the topological susceptibility diverges in the continuum limit \cite{berg1981}. This issue has motivated the application of the ``gradient flow'', a smoothing of high-frequency modes. We study the effect of the gradient flow on this divergence, finding that it persists as a logarithmic divergence. This result supports a previous study \cite{bietenholz2018} and indicates that either the definition of topological charge is problematic or the NLSM has no well-defined continuum limit. We also study the nontrivial field theory by introducing a $\theta$-term into the action and analyze the topological charge as a function of $\theta$ under the gradient flow.

\end{abstract}

\pagenumbering{arabic}

\chapter{Introduction}
\input{intro.tex}
\chapter{Theory}
\input{theory.tex}
\chapter{Methods}
\label{sec:methods}
\input{methods.tex}
\chapter{Results}
\input{results.tex}
\chapter{Conclusion \& Outlook}
\input{conclusion.tex}
\appendix
\chapter{C++ NLSM Monte Carlo Program}
\lstset{language=C++,
                basicstyle=\scriptsize\ttfamily,
                keywordstyle=\color{blue}\ttfamily,
                stringstyle=\color{red}\ttfamily,
                commentstyle=\color{green}\ttfamily,
                morecomment=[l][\color{magenta}]{\#},
                breaklines=true,
                postbreak=\mbox{\textcolor{red}{$\hookrightarrow$}\space}
}

\codeexample{sweep.h}
\codeexample{sweep.cpp}
\codeexample{lattice.h}
\codeexample{lattice.cpp}
\codeexample{phi.h}
\codeexample{phi.cpp}
\codeexample{observables.h}
\codeexample{constants.h}

%\bibliographystyle{unsrt}
%\bibliography{library}

\printbibliography[heading=bibintoc]

\end{document}

>>>>

\documentclass[12pt]{report}
\usepackage{amsmath}
\usepackage{bbm}
\usepackage{amsfonts}

@@

@@

\begin{document}
\begin{abstract}
\setcounter{page}{5}
\addcontentsline{toc}{chapter}{Abstract}
\paragraph
\indent The $O(3)$ non-linear sigma model (NLSM) is a prototypical field theory for QCD and ferromagnetism, featuring topological qualities. Though the topological susceptibility $\chi_t$ should vanish in physical theories, lattice simulations of the NLSM find that $\chi_t$ diverges in the continuum limit. We study the effect of the gradient flow on this quantity using a Markov Chain Monte Carlo method, finding that a logarithmic divergence persists. This result supports a previous study and indicates that either the definition of topological charge is problematic or the NLSM has no well-defined continuum limit. We also introduce a $\theta$-term and analyze the topological charge as a function of $\theta$ under the gradient flow.

\end{abstract}
\end{document}
